Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-03-14 analysis/memo_TAS_reviewers.Rmd
added figures for 80% and 90% credible intervals to Appendix

5. Choosing a credible interval amounts to deciding how conservative one wishes to be about inferring bias from past strike data, because we define bias "detection" narrowly to mean when the posterior for the bias parameter falls outside the chosen credible interval. Thus, the larger the credible interval one chooses, the greater the chance that zero falls within it. For clarity, we now focus on one credible interval (95%) in the paper and have placed simulation results based on other credible intervals in the Appendix.

>>>>

5. Choosing a credible interval amounts to deciding how conservative one wishes to be about inferring bias from past strike data, because we define bias "detection" narrowly to mean when the posterior for the bias parameter falls outside the chosen credible interval. Thus, the larger the credible interval one chooses, the greater the chance that zero falls within it. For clarity, we now focus on one credible interval (95%) in the paper and have placed simulation results based on 90% and 80% credible intervals in the Appendix.

### 2023-03-14 analysis/paper_draft3.Rmd
added figures for 80% and 90% credible intervals to Appendix

## Model Performance on Simulated Data

@@

Using a wider credible interval lowers this chance of error. For example, with a 90\% credible interval (not shown), when $b_{curr}=2$, the bias-detection rate is lower than with an 80\% credible interval; when $b_{curr}=0$, that detection rate is higher. The tradeoff is lower accuracy. With a 90\% credible interval, when the bias parameter is 2, the model is less accurate in detecting bias. When the bias parameter is 3, however, the detection rate is still high.

@@

Here, we extend the discussion in section \@ref(prototype) by discussing data collection and presenting additional illustrations of how a lawyer might use the prototype app.

## Data Collection

To collect this historical strike data, one of us filed a request with the U.S. District Court of Connecticut based on 28 U.S.C. $\S$ 1868.  Thereafter, we received copies of certain jury-selection records associated with twenty-nine criminal cases in that court during this period. These included strike sheets that indicated the identification number of prospective jurors who were struck by peremptory challenge, the order in which they were struck, and which side (prosecutor or defense) struck which juror. Such records also included a tally of answers to juror questionnaires that asked each prospective juror to report their race and gender.

@@

## Additional Illustrations

@@

```{r figapp4, out.width='75%', fig.cap = "Density Plots with Historical Strike Data (Gender). Screenshot of R-Shiny application show density plots based on historical and current strike data for prosecutor and defense attorney. Minimal weight ($a = 0.1$) applied to historical data.", fig.align='center', eval=FALSE}

load_path <- here::here("figures","batson_app_screenshots", "batson_app_screenshot4.png")

knitr::include_graphics(load_path)

>>>>

## Model Performance on Simulated Data {#simulation-results}

@@

The choice of credible interval also affects bias detection. For example, with a 90\% credible interval, when $b_{curr}=2$, the bias-detection rate is lower than with an 80\% credible interval; when $b_{curr}=0$, that detection rate is higher. The tradeoff is lower accuracy. With a 90\% credible interval, when the bias parameter is 2, the model is less accurate in detecting bias. When the bias parameter is 3, however, the detection rate is still high. For details on simulation results for 90% and 80% credible intervals, see the Appendix.

@@

Here, we extend section \@ref(simulation-results) by reporting our simulation results for 90% and 80% credible intervals.  We also extend the discussion in section \@ref(prototype) by discussing data collection and presenting additional illustrations of how a lawyer might use the prototype app.

## Bias Detection with 90% and 80% Credible Intervals

The choice of credible interval can affect bias detection as we define it, because the larger the credible interval one chooses, the greater the chance that zero falls within it, and vice-versa.  Here, we report simulation results for bias detection for 90% and 80% credible intervals for trials with fifteen, ten, and six strikes per side.

```{r figbd9015, out.width = "95%", fig.cap = "Bias Detection Rates, 90 pct credible interval, 15 strike scenario", fig.align='center'}

load_path <- here::here("figures","pp15_90CI.png")
knitr::include_graphics(load_path)

```{r figbd9010, out.width = "95%", fig.cap = "Bias Detection Rates (90 pct credible interval, 10 strikes scenario)", fig.align='center'}

load_path <- here::here("figures","pp10_90CI.png")
knitr::include_graphics(load_path)

```{r figbd906, out.width = "95%", fig.cap = "Bias Detection Rates based on 90 pct credible interval for 6 strike scenario", fig.align='center'}

load_path <- here::here("figures","pp6_90CI.png")
knitr::include_graphics(load_path)

```{r figbd8015, out.width = "95%", fig.cap = "Bias Detection Rates, 80 pct credible interval, 15 strike scenario", fig.align='center'}

load_path <- here::here("figures","pp15_80CI.png")
knitr::include_graphics(load_path)

```{r figbd8010, out.width = "95%", fig.cap = "Bias Detection Rates (80 pct credible interval, 10 strikes scenario)", fig.align='center'}

load_path <- here::here("figures","pp10_80CI.png")
knitr::include_graphics(load_path)

```{r figbd806, out.width = "95%", fig.cap = "Bias Detection Rates based on 80 pct credible interval for 6 strike scenario", fig.align='center'}

load_path <- here::here("figures","pp6_80CI.png")
knitr::include_graphics(load_path)

## Prototype Software Application

### Data Collection

To collect the historical strike data for the prototype software application, one of us filed a request with the U.S. District Court of Connecticut based on 28 U.S.C. $\S$ 1868.  Thereafter, we received copies of certain jury-selection records associated with twenty-nine criminal cases in that court during this period. These included strike sheets that indicated the identification number of prospective jurors who were struck by peremptory challenge, the order in which they were struck, and which side (prosecutor or defense) struck which juror. Such records also included a tally of answers to juror questionnaires that asked each prospective juror to report their race and gender.

@@

### Additional Illustrations

@@
